Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-04-11 paper/tex/sections/methods.tex
update rate explanation

\subsubsection{Detection rate calculation}
For each physics variation model, we compute the total number of merging DCOs in the Milky Way today based on the COMPAS simulation. This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy size and only sample from massive stars rather than the full IMF.

We determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7 and dividing by the total weights in the simulation. We multiply this fraction by the total number in the Milky Way to find a detection rate.
\begin{equation}
    N_{\rm detect} = \frac{\sum_{i = 0}^{N_{\rm detect}} w_i}{\sum_{i = 0}^{N_{\rm DCO}} w_i} \cdot N_{\rm MW}
\end{equation}
For a more in-depth discussion of this normalisation process see Appendix~\ref{app:rate_normalisation}.

>>>>

\subsubsection{Detection rate calculation}
For each physics variation model, we compute the total number of merging DCOs in the Milky Way today based on the COMPAS simulation. This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy size and only sample from massive stars rather than the full IMF. For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.

We determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7 and dividing by the total weights in the simulation. We multiply this fraction by the total number in the Milky Way to find a detection rate.
\begin{equation}
    N_{\rm detect} = \frac{\sum_{i = 0}^{N_{\rm detect}} w_i}{\sum_{i = 0}^{N_{\rm DCO}} w_i} \cdot N_{\rm MW}
\end{equation}
We calculate this detection rate by Monte Carlo sampling 2500 Milky Way instances (each containing 100,000 DCOs) for each DCO type and every physics variation in order to obtain values for the uncertainty on the expected detection rate.
